An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2021-12-22 simplified_sdc_intro/paper.tex
some more text

@@

Do this in 1-d
Show the amount of work needed for Strang vs. SDC

Play around with the threshold where NSE kicks in

>>>>

\newcommand{\atolspec}{{\epsilon_\mathrm{abs,spec}}}
\newcommand{\rtolspec}{{\epsilon_\mathrm{rel,spec}}}
\newcommand{\atolener}{{\epsilon_\mathrm{abs,ener}}}
\newcommand{\rtolener}{{\epsilon_\mathrm{rel,ener}}}

@@

We do a suite of runs with both Strang and the simplified-SDC
integration, using CFL numbers of 0.2, 0.4, and 0.8 and reaction
network tolerances of $\atolspec = \rtolspec = 10^{-5}$ and $\atolener
= \rtolener = 10^{-6}$.  We also run two sets with tighter tolerances.
The runs labeled ``mixed\_tols'' have $\atolspec = 10^{-8}$ and the runs
labeled ``tol1.e-6'' have $\atolspec = \rtolspec = 10^{-6}$, with the other
tolerances unchanged.

Overview plots of CFL = 0.8

Nonaka plots

Zoom panels showing different runs

Mass of different species (as a plot)

1-d slices along x=0?
